---
title: "DD Calf Weekly Data Collection"
subtitle: "Reference Page"
author: "Crystal Maiden"
format: 
  html: 
    theme: Cerulean
editor: visual
date: "`r Sys.Date()`"
execute: 
  eval: true
  echo: false
warning: false
---

Upload Data Monday so reports are up to date on Tuesday Morning

HERD ID: **93247057**

HERD Name: **StandardCalf**

Run **ALTER\\9** before data collection - as of last weeks upload all were 0, but still needs to be checked

Save New Data to: **R \> GitProjects \> DDCalf_WeeklyUploads \> DDCalf_NewData**

-   Replace Existing Files: (change formatting on ID & EID columns to *number*)
    -   DD_TOGROWR
    -   DD_RMVD
    -   DD_TP
    -   DD_WEAN
    -   DD_DZ
        -   Once DZ data is saved, run **EVENTS\\5**, compare disease events collected to counts for current month, if any discrepancies, add appropriate number to command line, and rerun. Update command line in Zoho Task.
        -   As of Previous weeks data, Events include: **FEVER, DIARHEA, LAME, NAVEL, PINKEYE, EARS, PNEUMON, MYCO**

Once new data is saved, run "DDCalf_Weekly Data Review.qmd"

```{r}
#| warning: false
#| echo: false
#read in r packages

library(tidyverse)
```

```{r}
#| label: read in csv's containing previous weeks data
DD_TOGROWR_Prev <- read.csv('~/R/GitProjects/DDCalf_weeklyUploads/DDCalf_PrevData/DD_TOGROWR.csv') 
  
DD_RMVD_Prev <- read.csv('~/R/GitProjects/DDCalf_weeklyUploads/DDCalf_PrevData/DD_RMVD.csv') 

DD_WEAN_Prev <- read.csv('~/R/GitProjects/DDCalf_weeklyUploads/DDCalf_PrevData/DD_WEAN.csv')

DD_TP_Prev <- read.csv('~/R/GitProjects/DDCalf_weeklyUploads/DDCalf_PrevData/DD_TP.csv')

DD_DZ_Prev <- read.csv('~/R/GitProjects/DDCalf_weeklyUploads/DDCalf_PrevData/DD_DZ.csv')

```

```{r}
#| label: data clean - previous weeks data

DD_TOGROWR_Prev_cln <- DD_TOGROWR_Prev %>% 
  distinct() %>% 
  mutate(Date = as.Date(Date))

DD_RMVD_Prev_cln <- DD_RMVD_Prev %>% 
  distinct() %>% 
  mutate(Date = as.Date(Date))

DD_WEAN_Prev_cln <- DD_WEAN_Prev %>% 
  distinct() %>% 
  mutate(Date = as.Date(Date))

DD_TP_Prev_cln <- DD_TP_Prev %>% 
  distinct() %>% 
  mutate(Date = as.Date(Date))

DD_DZ_Prev_cln <- DD_DZ_Prev %>% 
  distinct() %>% 
  mutate(Date = as.Date(Date))

```

```{r}
#| label: Previous Data Min and Max Dates

DD_TOGROWR_PrevStart <- format(min(DD_TOGROWR_Prev_cln$Date),"%m/%d/%Y")
  
DD_TOGROWR_PrevEnd <- format(max(DD_TOGROWR_Prev_cln$Date), "%m/%d/%Y")

DD_RMVD_PrevStart <- format(min(DD_RMVD_Prev_cln$Date),"%m/%d/%Y")
  
DD_RMVD_PrevEnd <- format(max(DD_RMVD_Prev_cln$Date), "%m/%d/%Y")

DD_TP_PrevStart <- format(min(DD_TP_Prev_cln$Date),"%m/%d/%Y")
  
DD_TP_PrevEnd <- format(max(DD_TP_Prev_cln$Date), "%m/%d/%Y")

DD_WEAN_PrevStart <- format(min(DD_WEAN_Prev_cln$Date),"%m/%d/%Y")
  
DD_WEAN_PrevEnd <- format(max(DD_WEAN_Prev_cln$Date), "%m/%d/%Y")

DD_DZ_PrevStart <- format(min(DD_DZ_Prev_cln$Date),"%m/%d/%Y")
  
DD_DZ_PrevEnd <- format(max(DD_DZ_Prev_cln$Date), "%m/%d/%Y")
```

## Data Uploaded Previous Week

TOGROWR: **`r DD_TOGROWR_PrevStart`** to **`r DD_TOGROWR_PrevEnd`**

RMVD: **`r DD_RMVD_PrevStart`** to **`r DD_RMVD_PrevEnd`**

TP: **`r DD_TP_PrevStart`** to **`r DD_TP_PrevEnd`**

WEAN: **`r DD_WEAN_PrevStart`** to **`r DD_WEAN_PrevEnd`**

DZ: **`r DD_DZ_PrevStart`** to **`r DD_DZ_PrevEnd`**
