---
title: "DD Calf Weekly Data Collection"
author: "Crystal Maiden"
format: html
editor: visual
echo: false
warning: false
---

```{r}
#| warning: false
#read in r packages

library(tidyverse)
library(gt)
library(shiny)
library(htmltools)
```
```{r}
#| label: todays date
#todays date

today <- format(Sys.Date(),"%m.%d.%Y")
```


```{r}
#| label: read in csv's containing previous weeks data

DD_TOGROWR_Prev <- read.csv('~/R/GitProjects/DDCalf_weeklyUploads/DDCalf_PrevData/DD_TOGROWR.csv') 
  
DD_RMVD_Prev <- read.csv('~/R/GitProjects/DDCalf_weeklyUploads/DDCalf_PrevData/DD_RMVD.csv') 

DD_WEAN_Prev <- read.csv('~/R/GitProjects/DDCalf_weeklyUploads/DDCalf_PrevData/DD_WEAN.csv')

DD_TP_Prev <- read.csv('~/R/GitProjects/DDCalf_weeklyUploads/DDCalf_PrevData/DD_TP.csv')

DD_DZ_Prev <- read.csv('~/R/GitProjects/DDCalf_weeklyUploads/DDCalf_PrevData/DD_DZ.csv')

```

```{r}
#| label: data clean - previous weeks data

DD_TOGROWR_Prev_cln <- DD_TOGROWR_Prev %>% 
  distinct() %>% 
  mutate(Date = mdy(Date))

DD_RMVD_Prev_cln <- DD_RMVD_Prev %>% 
  distinct() %>% 
  mutate(Date = mdy(Date))

DD_WEAN_Prev_cln <- DD_WEAN_Prev %>% 
  distinct() %>% 
  mutate(Date = mdy(Date))

DD_TP_Prev_cln <- DD_TP_Prev %>% 
  distinct() %>% 
  mutate(Date = mdy(Date))

DD_DZ_Prev_cln <- DD_DZ_Prev %>% 
  distinct() %>% 
  mutate(Date = mdy(Date))

```

```{r}
#| label: Previous Data Min and Max Dates

DD_TOGROWR_PrevStart <- format(min(DD_TOGROWR_Prev_cln$Date),"%m/%d/%Y")
  
DD_TOGROWR_PrevEnd <- format(max(DD_TOGROWR_Prev_cln$Date), "%m/%d/%Y")

DD_RMVD_PrevStart <- format(min(DD_RMVD_Prev_cln$Date),"%m/%d/%Y")
  
DD_RMVD_PrevEnd <- format(max(DD_RMVD_Prev_cln$Date), "%m/%d/%Y")

DD_TP_PrevStart <- format(min(DD_TP_Prev_cln$Date),"%m/%d/%Y")
  
DD_TP_PrevEnd <- format(max(DD_TP_Prev_cln$Date), "%m/%d/%Y")

DD_WEAN_PrevStart <- format(min(DD_WEAN_Prev_cln$Date),"%m/%d/%Y")
  
DD_WEAN_PrevEnd <- format(max(DD_WEAN_Prev_cln$Date), "%m/%d/%Y")

DD_DZ_PrevStart <- format(min(DD_DZ_Prev_cln$Date),"%m/%d/%Y")
  
DD_DZ_PrevEnd <- format(max(DD_DZ_Prev_cln$Date), "%m/%d/%Y")
```

## Data Uploaded Previous Week

TOGROWR: **`r DD_TOGROWR_PrevStart`** to **`r DD_TOGROWR_PrevEnd`**

RMVD: **`r DD_RMVD_PrevStart`** to **`r DD_RMVD_PrevEnd`**

TP: **`r DD_TP_PrevStart`** to **`r DD_TP_PrevEnd`**

WEAN: **`r DD_WEAN_PrevStart`** to **`r DD_WEAN_PrevEnd`**

DZ: **`r DD_DZ_PrevStart`** to **`r DD_DZ_PrevEnd`**

```{r}
#| label: read in csv's containing this weeks data

DD_TOGROWR_New <- read.csv('~/R/GitProjects/DDCalf_weeklyUploads/DDCalf_NewData/DD_TOGROWR.csv') 
  
DD_RMVD_New <- read.csv('~/R/GitProjects/DDCalf_weeklyUploads/DDCalf_NewData/DD_RMVD.csv') 

DD_WEAN_New <- read.csv('~/R/GitProjects/DDCalf_weeklyUploads/DDCalf_NewData/DD_WEAN.csv')

DD_TP_New <- read.csv('~/R/GitProjects/DDCalf_weeklyUploads/DDCalf_NewData/DD_TP.csv')

DD_DZ_New <- read.csv('~/R/GitProjects/DDCalf_weeklyUploads/DDCalf_NewData/DD_DZ.csv')

```

```{r}
#| label: data clean - this weeks data

DD_TOGROWR_New_cln <- DD_TOGROWR_New %>% 
  distinct() %>% 
  mutate(Date = mdy(Date))

DD_RMVD_New_cln <- DD_RMVD_New %>% 
  distinct() %>% 
  mutate(Date = mdy(Date))

DD_WEAN_New_cln <- DD_WEAN_New %>% 
  distinct() %>% 
  mutate(Date = mdy(Date))

DD_TP_New_cln <- DD_TP_New %>% 
  distinct() %>% 
  mutate(Date = mdy(Date))

DD_DZ_New_cln <- DD_DZ_New %>% 
  distinct() %>% 
  mutate(Date = mdy(Date))

```

```{r}
#| label: New Data Min and Max Dates

DD_TOGROWR_NewStart <- format(min(DD_TOGROWR_New_cln$Date),"%m/%d/%Y")
  
DD_TOGROWR_NewEnd <- format(max(DD_TOGROWR_New_cln$Date), "%m/%d/%Y")

DD_RMVD_NewStart <- format(min(DD_RMVD_New_cln$Date),"%m/%d/%Y")
  
DD_RMVD_NewEnd <- format(max(DD_RMVD_New_cln$Date), "%m/%d/%Y")

DD_TP_NewStart <- format(min(DD_TP_New_cln$Date),"%m/%d/%Y")
  
DD_TP_NewEnd <- format(max(DD_TP_New_cln$Date), "%m/%d/%Y")

DD_WEAN_NewStart <- format(min(DD_WEAN_New_cln$Date),"%m/%d/%Y")
  
DD_WEAN_NewEnd <- format(max(DD_WEAN_New_cln$Date), "%m/%d/%Y")

DD_DZ_NewStart <- format(min(DD_DZ_New_cln$Date),"%m/%d/%Y")
  
DD_DZ_NewEnd <- format(max(DD_DZ_New_cln$Date), "%m/%d/%Y")
```

## New Data Collected this Week

TOGROWR: **`r DD_TOGROWR_NewStart`** to **`r DD_TOGROWR_NewEnd`**

RMVD: **`r DD_RMVD_NewStart`** to **`r DD_RMVD_NewEnd`**

TP: **`r DD_TP_NewStart`** to **`r DD_TP_NewEnd`**

WEAN: **`r DD_WEAN_NewStart`** to **`r DD_WEAN_NewEnd`**

DZ: **`r DD_DZ_NewStart`** to **`r DD_DZ_NewEnd`**

# Data Comparisons

## TOGROWR
```{r}
#| label: TOGROWR Data Compare & Upload Data Setup

#sets up TOGROWR data for comparison tables

PrevTOGROWRCount <- 
  DD_TOGROWR_Prev_cln %>% 
    group_by(Date) %>% 
    summarise(PrevTOGROWR = n())

NewTOGROWRCount <- 
  DD_TOGROWR_New_cln %>% 
    group_by(Date) %>% 
    summarise(NewTOGROWR = n())

CombinedTOGROWR <-
  full_join(PrevTOGROWRCount,NewTOGROWRCount, by = "Date") %>% 
  mutate(Diff = PrevTOGROWR - NewTOGROWR)

#sets up TOGROWR data for upload table 

TOGROWR_Upload <- DD_TOGROWR_New_cln %>% 
                    anti_join(DD_TOGROWR_Prev_cln, 
                    join_by("ID","EID","SFID","BDAT","GNDR","Date")) %>% 
                    mutate(Remark = case_when(is.na(Remark) ~ "",
                                              TRUE ~ Remark),
                           Protocols = case_when(is.na(Protocols) ~ "",
                                                 TRUE ~ Protocols),
                           Technician = case_when(is.na(Technician) ~ "",
                                                  TRUE ~ Technician))
#creates TOGROWR Upload File

TOGROWR_Upload %>% 
  write.csv(paste0("~/R/GitProjects/DDCalf_WeeklyUploads/DDCalf_UploadFiles/DD_TOGROWR_",today,".csv"),row.names = FALSE)

#establish start date for TOGROWR New previous data file

TOGROWR_New_Prev_StartDate <- min(TOGROWR_Upload$Date)

#establish data for TOGROWR new previous data file

TOGROWR_New_Prev <- DD_TOGROWR_New_cln %>% 
                      filter(Date >= TOGROWR_New_Prev_StartDate)

#creates Temporary TOGROWR Prev File

TOGROWR_New_Prev %>% 
  write.csv(paste0("~/R/GitProjects/DDCalf_WeeklyUploads/DDCalf_PrevData/DD_TOGROWR_PREV_",today,".csv"),row.names = FALSE)

#formatting for TOGROWR display tables

TOGROWRtable <-
  CombinedTOGROWR %>% 
    gt() %>% 
      tab_header(title = "Compare")%>% 
      tab_style(
        cell_text(weight = "bold"),
        locations = cells_title(groups = "title")) %>% 
      fmt_date(
        columns = Date,
        date_style = 18) %>% 
      cols_label(PrevTOGROWR = "Prev",
                 NewTOGROWR = "New") %>% 
      cols_align(
        align = "center",
        columns = everything()) %>% 
      tab_style(
        style = cell_text(color = "red", weight = "bold"),
        locations = cells_body(
        column = vars(Diff),
        rows = Diff != 0)) %>% 
      tab_style(
        style = cell_text(color = "lightgrey"),
        locations = cells_body(
          column = vars(Diff),
          rows = Diff == 0)) %>% 
      tab_style(
         style = cell_text(color = "lightgrey"),
         locations = cells_body(
           column = vars(Diff),
           rows = is.na(Diff))) %>% 
      tab_style(
         style = cell_text(color = "lightgrey"),
         locations = cells_body(
           column = vars(PrevTOGROWR),
           rows = is.na(PrevTOGROWR)))

TOGROWR_Upload_Table <- 
  TOGROWR_Upload %>% 
    group_by(Date) %>% 
    summarise(Count = n()) %>% 
    gt() %>% 
      tab_header(title = "New Upload") %>% 
      tab_style(
        cell_text(weight = "bold"),
        locations = cells_title(groups = "title")) %>% 
      fmt_date(
        columns = Date,
        date_style = 18) %>% 
      cols_align(
        align = "center",
        columns = everything())

TOGROWR_NewPrev_Table <- 
  TOGROWR_New_Prev %>% 
    group_by(Date) %>% 
    summarise(Count = n()) %>% 
    gt() %>% 
      tab_header(title = "New Prev File") %>% 
      tab_style(
        cell_text(weight = "bold"),
        locations = cells_title(groups = "title")) %>% 
      fmt_date(
        columns = Date,
        date_style = 18) %>% 
      cols_align(
        align = "center",
        columns = everything())

htmltools::div(
  htmltools::div(gt::as_raw_html(TOGROWRtable), style = "float: left; width: 35%; margin-right: 0; padding-right: 0%;"),
  htmltools::div(gt::as_raw_html(TOGROWR_Upload_Table), style = "float: left; width: 25%; margin-left: 0; padding-left: 0%;"),
  htmltools::div(gt::as_raw_html(TOGROWR_NewPrev_Table), style = "float: left; width: 25%; margin-right: 0; padding-right: 0%;"))

```


## RMVD
```{r}
#| label: RMVD Data Compare & Upload Data Setup

#sets up RMVD data for comparison tables

PrevRMVDCount <- 
  DD_RMVD_Prev_cln %>% 
    group_by(Date) %>% 
    summarise(PrevRMVD = n())

NewRMVDCount <- 
  DD_RMVD_New_cln %>% 
    group_by(Date) %>% 
    summarise(NewRMVD = n())

CombinedRMVD <-
  full_join(PrevRMVDCount,NewRMVDCount, by = "Date") %>% 
  mutate(Diff = PrevRMVD - NewRMVD)

#sets up RMVD data for upload table 

RMVD_Upload <- DD_RMVD_New_cln %>% 
                    anti_join(DD_RMVD_Prev_cln, 
                    join_by("ID","Date")) %>%                   #need to add EID back in
                    mutate(Remark = case_when(is.na(Remark) ~ "",
                                              TRUE ~ Remark),
                           Protocols = case_when(is.na(Protocols) ~ "",
                                                 TRUE ~ Protocols),
                           Technician = case_when(is.na(Technician) ~ "",
                                                  TRUE ~ Technician))
#creates RMVD Upload File

RMVD_Upload %>% 
  write.csv(paste0("~/R/GitProjects/DDCalf_WeeklyUploads/DDCalf_UploadFiles/DD_RMVD_",today,".csv"),row.names = FALSE)

#establish start date for RMVD New previous data file

RMVD_New_Prev_StartDate <- min(RMVD_Upload$Date)

#establish data for RMVD new previous data file

RMVD_New_Prev <- DD_RMVD_New_cln %>% 
                      filter(Date >= RMVD_New_Prev_StartDate)

#creates Temporary RMVD Prev File

RMVD_New_Prev %>% 
  write.csv(paste0("~/R/GitProjects/DDCalf_WeeklyUploads/DDCalf_PrevData/DD_RMVD_PREV_",today,".csv"),row.names = FALSE)

#formatting for RMVD display tables

RMVDtable <-
  CombinedRMVD %>% 
    gt() %>% 
      tab_header(title = "Compare")%>% 
      tab_style(
        cell_text(weight = "bold"),
        locations = cells_title(groups = "title")) %>% 
      fmt_date(
        columns = Date,
        date_style = 18) %>% 
      cols_label(PrevRMVD = "Prev",
                 NewRMVD = "New") %>% 
      cols_align(
        align = "center",
        columns = everything()) %>% 
      tab_style(
        style = cell_text(color = "red", weight = "bold"),
        locations = cells_body(
        column = vars(Diff),
        rows = Diff != 0)) %>% 
      tab_style(
        style = cell_text(color = "lightgrey"),
        locations = cells_body(
          column = vars(Diff),
          rows = Diff == 0)) %>% 
      tab_style(
         style = cell_text(color = "lightgrey"),
         locations = cells_body(
           column = vars(Diff),
           rows = is.na(Diff))) %>% 
      tab_style(
         style = cell_text(color = "lightgrey"),
         locations = cells_body(
           column = vars(PrevRMVD),
           rows = is.na(PrevRMVD)))

RMVD_Upload_Table <- 
  RMVD_Upload %>% 
    group_by(Date) %>% 
    summarise(Count = n()) %>% 
    gt() %>% 
      tab_header(title = "New Upload") %>% 
      tab_style(
        cell_text(weight = "bold"),
        locations = cells_title(groups = "title")) %>% 
      fmt_date(
        columns = Date,
        date_style = 18) %>% 
      cols_align(
        align = "center",
        columns = everything())

RMVD_NewPrev_Table <- 
  RMVD_New_Prev %>% 
    group_by(Date) %>% 
    summarise(Count = n()) %>% 
    gt() %>% 
      tab_header(title = "New Prev File") %>% 
      tab_style(
        cell_text(weight = "bold"),
        locations = cells_title(groups = "title")) %>% 
      fmt_date(
        columns = Date,
        date_style = 18) %>% 
      cols_align(
        align = "center",
        columns = everything())

htmltools::div(
  htmltools::div(gt::as_raw_html(RMVDtable), style = "float: left; width: 35%; margin-right: 0; padding-right: 0%;"),
  htmltools::div(gt::as_raw_html(RMVD_Upload_Table), style = "float: left; width: 25%; margin-left: 0; padding-left: 0%;"),
  htmltools::div(gt::as_raw_html(RMVD_NewPrev_Table), style = "float: left; width: 25%; margin-right: 0; padding-right: 0%;"))

```
## TP
```{r}
#| label: TP Data Compare & Upload Data Setup

#sets up TP data for comparison tables

PrevTPCount <- 
  DD_TP_Prev_cln %>% 
    group_by(Date) %>% 
    summarise(PrevTP = n())

NewTPCount <- 
  DD_TP_New_cln %>% 
    group_by(Date) %>% 
    summarise(NewTP = n())

CombinedTP <-
  full_join(PrevTPCount,NewTPCount, by = "Date") %>% 
  mutate(Diff = PrevTP - NewTP)

#sets up TP data for upload table 

TP_Upload <- DD_TP_New_cln %>% 
                    anti_join(DD_TP_Prev_cln, 
                    join_by("ID","Date")) %>%                   #need to add EID back in
                    mutate(Protocols = case_when(is.na(Protocols) ~ "",
                                                 TRUE ~ Protocols),
                           Technician = case_when(is.na(Technician) ~ "",
                                                  TRUE ~ Technician))
#creates TP Upload File

TP_Upload %>% 
  write.csv(paste0("~/R/GitProjects/DDCalf_WeeklyUploads/DDCalf_UploadFiles/DD_TP_",today,".csv"),row.names = FALSE)

#establish start date for TP New previous data file

TP_New_Prev_StartDate <- min(TP_Upload$Date)

#establish data for TP new previous data file

TP_New_Prev <- DD_TP_New_cln %>% 
                      filter(Date >= TP_New_Prev_StartDate)

#creates Temporary TP Prev File

TP_New_Prev %>% 
  write.csv(paste0("~/R/GitProjects/DDCalf_WeeklyUploads/DDCalf_PrevData/DD_TP_PREV_",today,".csv"),row.names = FALSE)

#formatting for TP display tables

TPtable <-
  CombinedTP %>% 
    gt() %>% 
      tab_header(title = "Compare")%>% 
      tab_style(
        cell_text(weight = "bold"),
        locations = cells_title(groups = "title")) %>% 
      fmt_date(
        columns = Date,
        date_style = 18) %>% 
      cols_label(PrevTP = "Prev",
                 NewTP = "New") %>% 
      cols_align(
        align = "center",
        columns = everything()) %>% 
      tab_style(
        style = cell_text(color = "red", weight = "bold"),
        locations = cells_body(
        column = vars(Diff),
        rows = Diff != 0)) %>% 
      tab_style(
        style = cell_text(color = "lightgrey"),
        locations = cells_body(
          column = vars(Diff),
          rows = Diff == 0)) %>% 
      tab_style(
         style = cell_text(color = "lightgrey"),
         locations = cells_body(
           column = vars(Diff),
           rows = is.na(Diff))) %>% 
      tab_style(
         style = cell_text(color = "lightgrey"),
         locations = cells_body(
           column = vars(PrevTP),
           rows = is.na(PrevTP)))

TP_Upload_Table <- 
  TP_Upload %>% 
    group_by(Date) %>% 
    summarise(Count = n()) %>% 
    gt() %>% 
      tab_header(title = "New Upload") %>% 
      tab_style(
        cell_text(weight = "bold"),
        locations = cells_title(groups = "title")) %>% 
      fmt_date(
        columns = Date,
        date_style = 18) %>% 
      cols_align(
        align = "center",
        columns = everything())

TP_NewPrev_Table <- 
  TP_New_Prev %>% 
    group_by(Date) %>% 
    summarise(Count = n()) %>% 
    gt() %>% 
      tab_header(title = "New Prev File") %>% 
      tab_style(
        cell_text(weight = "bold"),
        locations = cells_title(groups = "title")) %>% 
      fmt_date(
        columns = Date,
        date_style = 18) %>% 
      cols_align(
        align = "center",
        columns = everything())

htmltools::div(
  htmltools::div(gt::as_raw_html(TPtable), style = "float: left; width: 35%; margin-right: 0; padding-right: 0%;"),
  htmltools::div(gt::as_raw_html(TP_Upload_Table), style = "float: left; width: 25%; margin-left: 0; padding-left: 0%;"),
  htmltools::div(gt::as_raw_html(TP_NewPrev_Table), style = "float: left; width: 25%; margin-right: 0; padding-right: 0%;"))

```
## WEAN
```{r}
#| label: WEAN Data Compare & Upload Data Setup

#sets up WEAN data for comparison tables

PrevWEANCount <- 
  DD_WEAN_Prev_cln %>% 
    group_by(Date) %>% 
    summarise(PrevWEAN = n())

NewWEANCount <- 
  DD_WEAN_New_cln %>% 
    group_by(Date) %>% 
    summarise(NewWEAN = n())

CombinedWEAN <-
  full_join(PrevWEANCount,NewWEANCount, by = "Date") %>% 
  mutate(Diff = PrevWEAN - NewWEAN)

#sets up WEAN data for upload table 

WEAN_Upload <- DD_WEAN_New_cln %>% 
                    anti_join(DD_WEAN_Prev_cln, 
                    join_by("ID","Date")) %>%                   #need to add EID back in
                    mutate(Protocols = case_when(is.na(Protocols) ~ "",
                                                 TRUE ~ Protocols),
                           Technician = case_when(is.na(Technician) ~ "",
                                                  TRUE ~ Technician))
#creates WEAN Upload File

WEAN_Upload %>% 
  write.csv(paste0("~/R/GitProjects/DDCalf_WeeklyUploads/DDCalf_UploadFiles/DD_WEAN_",today,".csv"),row.names = FALSE)

#establish start date for WEAN New previous data file

WEAN_New_Prev_StartDate <- min(WEAN_Upload$Date)

#establish data for WEAN new previous data file

WEAN_New_Prev <- DD_WEAN_New_cln %>% 
                      filter(Date >= WEAN_New_Prev_StartDate)

#creates Temporary WEAN Prev File

WEAN_New_Prev %>% 
  write.csv(paste0("~/R/GitProjects/DDCalf_WeeklyUploads/DDCalf_PrevData/DD_WEAN_PREV_",today,".csv"),row.names = FALSE)

#formatting for WEAN display tables

WEANtable <-
  CombinedWEAN %>% 
    gt() %>% 
      tab_header(title = "Compare")%>% 
      tab_style(
        cell_text(weight = "bold"),
        locations = cells_title(groups = "title")) %>% 
      fmt_date(
        columns = Date,
        date_style = 18) %>% 
      cols_label(PrevWEAN = "Prev",
                 NewWEAN = "New") %>% 
      cols_align(
        align = "center",
        columns = everything()) %>% 
      tab_style(
        style = cell_text(color = "red", weight = "bold"),
        locations = cells_body(
        column = vars(Diff),
        rows = Diff != 0)) %>% 
      tab_style(
        style = cell_text(color = "lightgrey"),
        locations = cells_body(
          column = vars(Diff),
          rows = Diff == 0)) %>% 
      tab_style(
         style = cell_text(color = "lightgrey"),
         locations = cells_body(
           column = vars(Diff),
           rows = is.na(Diff))) %>% 
      tab_style(
         style = cell_text(color = "lightgrey"),
         locations = cells_body(
           column = vars(PrevWEAN),
           rows = is.na(PrevWEAN)))

WEAN_Upload_Table <- 
  WEAN_Upload %>% 
    group_by(Date) %>% 
    summarise(Count = n()) %>% 
    gt() %>% 
      tab_header(title = "New Upload") %>% 
      tab_style(
        cell_text(weight = "bold"),
        locations = cells_title(groups = "title")) %>% 
      fmt_date(
        columns = Date,
        date_style = 18) %>% 
      cols_align(
        align = "center",
        columns = everything())

WEAN_NewPrev_Table <- 
  WEAN_New_Prev %>% 
    group_by(Date) %>% 
    summarise(Count = n()) %>% 
    gt() %>% 
      tab_header(title = "New Prev File") %>% 
      tab_style(
        cell_text(weight = "bold"),
        locations = cells_title(groups = "title")) %>% 
      fmt_date(
        columns = Date,
        date_style = 18) %>% 
      cols_align(
        align = "center",
        columns = everything())

htmltools::div(
  htmltools::div(gt::as_raw_html(WEANtable), style = "float: left; width: 35%; margin-right: 0; padding-right: 0%;"),
  htmltools::div(gt::as_raw_html(WEAN_Upload_Table), style = "float: left; width: 25%; margin-left: 0; padding-left: 0%;"),
  htmltools::div(gt::as_raw_html(WEAN_NewPrev_Table), style = "float: left; width: 25%; margin-right: 0; padding-right: 0%;"))

```
## DZ
```{r}
#| label: DZ Data Compare & Upload Data Setup

#sets up DZ data for comparison tables

PrevDZCount <- 
  DD_DZ_Prev_cln %>% 
    group_by(Date) %>% 
    summarise(PrevDZ = n())

NewDZCount <- 
  DD_DZ_New_cln %>% 
    group_by(Date) %>% 
    summarise(NewDZ = n())

CombinedDZ <-
  full_join(PrevDZCount,NewDZCount, by = "Date") %>% 
  mutate(Diff = PrevDZ - NewDZ)

#sets up DZ data for upload table 

DZ_Upload <- DD_DZ_New_cln %>% 
                    anti_join(DD_DZ_Prev_cln, 
                    join_by("ID","Date")) %>%                   #need to add EID back in
                    mutate(Protocols = case_when(is.na(Protocols) ~ "",
                                                 TRUE ~ Protocols),
                           Technician = case_when(is.na(Technician) ~ "",
                                                  TRUE ~ Technician))
#creates DZ Upload File

DZ_Upload %>% 
  write.csv(paste0("~/R/GitProjects/DDCalf_WeeklyUploads/DDCalf_UploadFiles/DD_DZ_",today,".csv"),row.names = FALSE)

#establish start date for DZ New previous data file

DZ_New_Prev_StartDate <- min(DZ_Upload$Date)

#establish data for DZ new previous data file

DZ_New_Prev <- DD_DZ_New_cln %>% 
                      filter(Date >= DZ_New_Prev_StartDate)

#creates Temporary DZ Prev File

DZ_New_Prev %>% 
  write.csv(paste0("~/R/GitProjects/DDCalf_WeeklyUploads/DDCalf_PrevData/DD_DZ_PREV_",today,".csv"),row.names = FALSE)

#formatting for DZ display tables

DZtable <-
  CombinedDZ %>% 
    gt() %>% 
      tab_header(title = "Compare")%>% 
      tab_style(
        cell_text(weight = "bold"),
        locations = cells_title(groups = "title")) %>% 
      fmt_date(
        columns = Date,
        date_style = 18) %>% 
      cols_label(PrevDZ = "Prev",
                 NewDZ = "New") %>% 
      cols_align(
        align = "center",
        columns = everything()) %>% 
      tab_style(
        style = cell_text(color = "red", weight = "bold"),
        locations = cells_body(
        column = vars(Diff),
        rows = Diff != 0)) %>% 
      tab_style(
        style = cell_text(color = "lightgrey"),
        locations = cells_body(
          column = vars(Diff),
          rows = Diff == 0)) %>% 
      tab_style(
         style = cell_text(color = "lightgrey"),
         locations = cells_body(
           column = vars(Diff),
           rows = is.na(Diff))) %>% 
      tab_style(
         style = cell_text(color = "lightgrey"),
         locations = cells_body(
           column = vars(PrevDZ),
           rows = is.na(PrevDZ)))

DZ_Upload_Table <- 
  DZ_Upload %>% 
    group_by(Date) %>% 
    summarise(Count = n()) %>% 
    gt() %>% 
      tab_header(title = "New Upload") %>% 
      tab_style(
        cell_text(weight = "bold"),
        locations = cells_title(groups = "title")) %>% 
      fmt_date(
        columns = Date,
        date_style = 18) %>% 
      cols_align(
        align = "center",
        columns = everything())

DZ_NewPrev_Table <- 
  DZ_New_Prev %>% 
    group_by(Date) %>% 
    summarise(Count = n()) %>% 
    gt() %>% 
      tab_header(title = "New Prev File") %>% 
      tab_style(
        cell_text(weight = "bold"),
        locations = cells_title(groups = "title")) %>% 
      fmt_date(
        columns = Date,
        date_style = 18) %>% 
      cols_align(
        align = "center",
        columns = everything())

htmltools::div(
  htmltools::div(gt::as_raw_html(DZtable), style = "float: left; width: 35%; margin-right: 0; padding-right: 0%;"),
  htmltools::div(gt::as_raw_html(DZ_Upload_Table), style = "float: left; width: 25%; margin-left: 0; padding-left: 0%;"),
  htmltools::div(gt::as_raw_html(DZ_NewPrev_Table), style = "float: left; width: 25%; margin-right: 0; padding-right: 0%;"))

```
### Once all data has been uploaded, comment out final section and rerun all script. 
```{r}
# # creates final Previous files
# TOGROWR_New_Prev %>%
#   write.csv("~/R/GitProjects/DDCalf_WeeklyUploads/DDCalf_PrevData/DD_TOGROWR.csv",row.names = FALSE)
# 
# RMVD_New_Prev %>%
#   write.csv("~/R/GitProjects/DDCalf_WeeklyUploads/DDCalf_PrevData/DD_RMVD.csv",row.names = FALSE)
# 
# TP_New_Prev %>%
#   write.csv("~/R/GitProjects/DDCalf_WeeklyUploads/DDCalf_PrevData/DD_TP.csv",row.names = FALSE)
# 
# WEAN_New_Prev %>%
#   write.csv("~/R/GitProjects/DDCalf_WeeklyUploads/DDCalf_PrevData/DD_WEAN.csv",row.names = FALSE)
# 
# DZ_New_Prev %>%
#   write.csv("~/R/GitProjects/DDCalf_WeeklyUploads/DDCalf_PrevData/DD_DZ.csv",row.names = FALSE)
```

